Refactoring `nls()`: a constructive critique

### 2023-02-03 RefactoringNLS/JNAB230203.Rmd
add model frame section
add sources of data section

>>>>

## Feature: model frame

`model` is an argument to the `nls()` function, which is documented as:

> **model** logical. If true, the model frame is returned as part of the object. Default is FALSE.

Indeed, the argument only gets used when `nls()` is about to return its result object, and the
element `model` is NULL unless the calling argument `model` is TRUE. (Using the same name could
be confusing.) However, the model frame is used within the function code in the form of the object
`mf`. We feel that users could benefit from more extensive documentation and examples of its use.

## Feature: Sources of data

`nls()` can be called without specifying the `data` argument. In this case, it will
search in the available environments (i.e., workspaces) for suitable data objects. 
We do NOT like this approach, but it is "the R way". R allows users to leave many 
objects in the default (`.GlobalEnv`) workspace. Moreover, users have to actively 
suppress saving this workspace (`.RData`) on exit; otherwise, any such file in the path, 
when R is launched, will be loaded. The overwhelming proportion of R users in our
acquaintance avoid saving the workspace because of the danger of lurking data and
functions which may cause unwanted results.

Nevertheless, to provide compatible behaviour with `nls()`, competing programs 
need to ensure equivalent behaviour, but users should test that the 
operation is as they intend.
